The robot who pretend-played with me

### 2017-04-06 paper.tex
Bits on the socio-cognitive framing of the freeplay sandbox

children can engage in open-ended and
non-directive play situations, yet sufficiently
defined to be reproducible; focus on abstract socio-cognitive facets (robot
perception and manipulation are simplified); well suited for qualitative and
quantitative analysis using metrics like Słowinski’s Individual Motor Signature
(for behavioural alignment), Ballard’s coding of children’s free-play
interactions, with-me-ness (for assessment of co-engagment).

@@

\subsection{Hypotheses}

>>>>

children can engage in open-ended and
non-directive play situations, yet sufficiently
defined to be reproducible;

\subsection{Socio-cognitive Framing}

focus on abstract socio-cognitive facets (robot
perception and manipulation are simplified); well suited for qualitative and
quantitative analysis using metrics like Słowinski’s Individual Motor Signature
(for behavioural alignment), Ballard’s coding of children’s free-play
interactions, with-me-ness (for assessment of co-engagment).

carefully framed: as far as possible, they ne-
cessitate only the cognitive capabilities that they ev-
idence (e.g. if they evidence a purely socio-linguistic
mechanism, they will not mandate complex action ca-
pabilities – they may benefit from it, though),

This point is especially important as it allows an
incremental path: a robot should be able to tackle one or
several of these task independently of the others, and a re-
search team may progressively extend their cognitive models
to incorporate more and more of the cognitive capabilities
required by the robot to address all of the tasks.

@@

\subsection{High level Hypotheses}

\begin{itemize}
    \item autonomous behaviour \emph{ensues from} 
\end{itemize}

\subsection{Operational Hypotheses}
